\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-02 draft.tex
update lit review with uncertainty lit

Another related literature considers the impact of exogenously-determined political uncertainty on the potential for trade cooperation. These studies (e.g. Feenstra and Lewis (1991); Milner and Rosendorff (2001); Bagwell and Staiger (2005); Beshkar (2010)) derive various implications for the design of international trade agreements using a Baldwin (1987)-style government welfare function with exogenous shocks to the political-pressure parameter. As explained in the next section, the model presented here is intended to be a bridge between this literature and that discussed above that focuses on endogenously-determined political economy weights. To preview, this model is closest to that of Bagwell and Staiger (2005), with two main changes: in place of their unitary government signing a trade agreement and having different preferences ex-ante and ex-post, this model has two branches of government with differing preferences, where---in the case of the legislature---the political economy weights are determined endogenously.

@@

@@

@@

@@

>>>>

Another related literature considers the impact of exogenously-determined political uncertainty on the potential for trade cooperation. These studies (e.g. Feenstra and Lewis (1991); Milner and Rosendorff (2001); Bagwell and Staiger (2005); Beshkar (2010); Horn, Maggi and Staiger (2010); Beshkar and Bond (2012); Amador and Bagwell (2013)) derive various implications for the design of international trade agreements using a Baldwin (1987)-style government welfare function with exogenous shocks to the political-pressure parameter. As explained in the next section, the model presented here is intended to be a bridge between this literature and that discussed above that focuses on endogenously-determined political economy weights. To preview, this model is closest to that of Bagwell and Staiger (2005), with two main changes: in place of their unitary government signing a trade agreement and having different preferences ex-ante and ex-post, this model has two branches of government with differing preferences, where---in the case of the legislature---the political economy weights are determined endogenously.

A very recent literature has begun to study the effects of trade agreements for reducing the uncertainty that firms (Handley 2014 and Handley and Lim\~{a}o 2015) and governments (Lim\~{a}o and Maggi 2015) face.

@@

\item Amador, M., and Bagwell, K., 2013. The Theory of Optimal Delegation with an Application to Tariff Caps. Econometrica 81, 1541-1599.

@@

\item Beshkar, M. and Bond, E., 2012. Cap and Escape in Trade Agreements. Available at \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2145679}.

@@

\item Handley, K., 2014. Exporting under Trade Policy Uncertainty: Theory and Evidence. Journal of international Economics 94, 50-66.

\item Handley, K., Lim\~{a}o, N., 2015. Trade and Investment under Policy Uncertainty: Theory and Firm Evidence. American Economic Journal: Economic Policy 7, 189-222.

@@

\item Lim\~{a}o, N., Maggi, G., 2015. Uncertainty and Trade Agreements. American Economic Journal: Microeconomics 7, 1-42.
